%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{DANIEL} \headerlastnamestyle{PALMA} \\
	\vspace{2mm}
	{\faEnvelope\ danivgy@gmail.com} | {\faLink\ linkedin.com/in/danthelion} | {\faLink\ github.com/danthelion} | {\faLink\ arecadata.com}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Brooklyn Data Co.}
	{Senior Data Engineer}
	{Mar 2022 – Present}
	{}
	{\begin{cvitems}
		\item {At BDC, I provide expert guidance to clients on the design and implementation of scalable and maintainable data-driven solutions.}
		\item {Architected and delivered a high-performance streaming data platform for a leading sports betting company.}
		\item {Constructed a user tracking data ingestion pipeline for a crisis support non-profit organization.}
		\item {Established the foundation for data analytics engineering at various small to medium-sized companies.}
		\end{cvitems}}
	\cventry
	{Aliz}
	{Senior Data Engineer}
	{Jan 2021 – Mar 2022}
	{}
	{\begin{cvitems}
		\item {Implemented a comprehensive Data Warehouse solution, including CDC integrations, a Data Lake, and a BI dashboard.}
		\item {Contributed to the development of a fully integrated Data Warehouse and Machine Learning recommendation system.}
		\item {Conducted training sessions on a range of software engineering and data engineering topics, as well as Google Cloud services, for internal and external stakeholders.}
		\item {Took part in the development of a self-serving Software-as-a-Service solution to streamline common infrastructure patterns and improve operational efficiency.}
		\end{cvitems}}
	\cventry
	{Synetiq}
	{Engineering Lead}
	{Jan 2019 – Jan 2020}
	{}
	{\begin{cvitems}
		\item {Proactively gathered and analyzed customer feedback to inform product strategy and roadmap.}
		\item {Managed technical requirements and budget planning for a multinational expansion.}
		\item {Developed technical strategy and led the implementation of enterprise-level software solutions.}
		\item {Provided technical mentorship and guidance to junior engineers, fostering a positive and inclusive team culture.}
		\item {Continuously assessed and optimized engineering processes and systems to drive efficiency and innovation.}
		\end{cvitems}}
	\cventry
	{Synetiq}
	{Data Engineer}
	{Oct 2016 – Jan 2019}
	{}
	{\begin{cvitems}
		\item {Designed and implemented data extraction, cleansing, aggregation and visualization solutions for biometric sensors including EEG, PPG, and eye tracking cameras.}
		\item {Migrated web services to a highly scalable, cloud-based container infrastructure using Kubernetes.}
		\item {Established fully automated continuous integration and deployment pipelines to support cloud native operations.}
		\item {Architected and deployed a B2B data visualization dashboard platform with end-to-end capabilities.}
		\item {Conducted user research and gathered insights through customer interviews and feedback.}
		\end{cvitems}}
	\cventry
	{Telenor}
	{Software Engineer}
	{Apr 2015 – Oct 2016}
	{}
	{\begin{cvitems}
		\item {Developed procedures for efficient extraction, transformation, and loading of telecommunication device configuration data.}
		\item {Created a web-based application to visualize time-series and geolocation data.}
		\item {Developed a web-based reporting and monitoring tool, driven by data analytics.}
		\item {Implemented automated stored procedures and ETL processes to streamline data management.}
		\end{cvitems}}
\end{cventries}
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Data Management: & {\skill{ Snowflake, BigQuery, Redshift, SQL, DuckDB, Databricks, SQL, Data Lakes, Looker }} \\
		Streaming Data: & {\skill{ Kafka, Flink, Redpanda, Debezium, CDC, Materialize }} \\
		Data Engineering: & {\skill{ dbt, Airflow, Dagster, Fivetran, Meltano }} \\
		Programming Languages: & {\skill { Python, Go, Shell Scripting }} \\
		Infrastructure Automation: & {\skill{ GCP, AWS, Terraform, Docker, Kubernetes, CI/CD, GNU/Linux }} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{BSc in Computer Science}
	{Eötvös Lóránd University}
	{Budapest, Hungary}
	{Sep 2014 – 2018}
	{}
\end{cventries}

\vspace{-2mm}
\ 
\end{document}
